---
title: "All page clean up"
subtitle: "with whiskyfun.com data"
author: "Tony Duan"

execute:
  warning: false
  error: false
  eval: false
format:
  html:
    toc: true
    toc-location: right
    code-fold: show
    code-tools: true
    number-sections: true
    code-block-bg: true
    code-block-border-left: "#31BAE9"
---


```{r}
library(tidyverse)
library(rvest)
library(stringr)
library(openxlsx)
library(readxl)
library(lubridate)
library(ggplot2)
```

```{r}
packageVersion("rvest")
```


# input


```{r}
data001=read_excel('./output/all_page_review_all_v2.xlsx')
```

```{r}
glimpse(data001)
```



```{r}
data002=data001%>% mutate(
  
  bottle_review2=bottle_review2%>% str_replace("–", "-")%>% str_replace("Palate", "Mouth")
  ,name=paste0(str_extract(bottle_review2, regex( "[^)]+")),")")
  ,distillery=bottle_review2 %>% str_extract(".*?\\d")%>% str_sub(end=-3)
  
  ,colour=(bottle_review2 %>% str_match("Colour:\\s*(.*?)\\s*\\."))[,2]
  ,nose=(bottle_review2 %>% str_match("Nose\\s*(.*?)\\s*Mouth"))[,2]
  ,mouth=(bottle_review2 %>% str_match("Mouth\\s*(.*?)\\s*Finish"))[,2]
  ,finish=(bottle_review2 %>% str_match("Finish:\\s*(.*?)\\s*Comments"))[,2]
  ,comments=(bottle_review2 %>% str_match("Comments:\\s*(.*?)\\s*SGP"))[,2]
  
  #,full_score=(bottle_review2 %>%str_match_all("[:digit:][:digit:][:space:]points."))%>% sapply(tail, 1)
  ,full_score=(bottle_review2 %>%str_match_all("[:digit:][:digit:][:space:]points."))%>% sapply(tail, 1)
  ,score=full_score %>% str_replace("points.","") %>% as.numeric()
  
  ,review_date=((str_match(old_page %>%str_to_lower(),"https://www.whiskyfun.com/archive\\s*(.*?)\\s*-"))[,2] )%>% str_to_title()
 
  ,review_date2= myd(review_date, truncated = 1)
  ,review_date2=if_else(is.na(review_date)==TRUE,today(),review_date2)
  
  ,review_year=year(review_date2)
) %>% unique()

glimpse(data002)
```

```{r}
cols=names(data002)
test001=data002 %>%filter(if_any(.cols = cols, .fns = ~is.na(.x)))
glimpse(test001)
```


```{r}
write.xlsx(data002,'./output/all_page_review_clean_v2.xlsx')
```



```{r}
test001=data002 %>% filter(bottle_review2 %>% str_sub(1,4)=='Nose'|bottle_review2 %>% str_sub(1,6)=='Colour'|bottle_review2 %>% str_sub(1,5)=='Mouth'|bottle_review2 %>% str_sub(1,6)=='Finish'|bottle_review2 %>% str_sub(1,8)=='Comments')
```







```{r}
glimpse(test001)
```


```{r}
test002=test001 %>% head()
```


```{r}
review_html_elements=".textegrandfoncegras , .TextenormalNEW, .Textenormal,td > font,div td font"

bottle_review_up1_list=c()
bottle_review_up2_list=c()

for (i in test002$bottle_review2){
  #print(i)
  link=(test002 %>% filter(bottle_review2==i))$old_page
  print(link)
  page=read_html(curl(link, handle = curl::new_handle("useragent" = "Mozilla/5.0")))
  bottle_review=page  %>% html_elements(review_html_elements) %>% html_text2()
  
  bottle_review=unique(bottle_review[bottle_review != ""])
  
  index_num=match(i,bottle_review)
  
  bottle_review_up1=bottle_review[index_num-1]
  bottle_review_up2=bottle_review[index_num-2]
  
  bottle_review_up1_list=c(bottle_review_up1_list,bottle_review_up1)
  bottle_review_up2_list=c(bottle_review_up2_list,bottle_review_up2)
}
```





# reference

%d = Day number of month (5, 17, 28, etc.)

%j = Day number of the year (Julian day 001-366)

%a = Abbreviated weekday (Mon, Tue, Wed, etc.)

%A = Full weekday (Monday, Tuesday, etc.) %w = Weekday number (0-6, Sunday is 0)

%u = Weekday number (1-7, Monday is 1)

%W = Week number (00-53, Monday is week start)

%U = Week number (01-53, Sunday is week start)

%m = Month number (e.g. 01, 02, 03, 04)

%b = Abbreviated month (Jan, Feb, etc.)

%B = Full month (January, February, etc.)

%y = 2-digit year (e.g. 89)

%Y = 4-digit year (e.g. 1989)

%h = hours (24-hr clock)

%m = minutes

%s = seconds %z = offset from GMT

%Z = Time zone (character)


https://epirhandbook.com/en/working-with-dates.html
