---
title: "Data table"


execute:
  warning: false
  error: false
format:
  html:
    toc: true
    toc-location: right
    code-fold: show
    code-tools: true
    number-sections: true
    code-block-bg: true
    code-block-border-left: "#31BAE9"
---

# Data table with GT package

![](https://gt.rstudio.com/reference/figures/logo.svg){width="200"}

With the gt package, anyone can make wonderful-looking tables using the R programming language. The gt philosophy: we can construct a wide variety of useful tables with a cohesive set of table parts. These include the table header, the stub, the column labels and spanner column labels, the table body, and the table footer.

![](https://gt.rstudio.com/reference/figures/gt_parts_of_a_table.svg)

![](https://gt.rstudio.com/reference/figures/gt_workflow_diagram.svg)

```{r}
library(gt)
```


```{r}
library(gt)
library(gtExtras)

# Define the start and end dates for the data range
start_date <- "2010-06-07"
end_date <- "2010-06-14"

# Create a gt table based on preprocessed
# `sp500` table data
sp500 |>
  dplyr::filter(date >= start_date & date <= end_date) |>
  dplyr::select(-adj_close) |>
  gt() |>
  tab_header(
    # title
    title = "S&P 500",
    # subtitle
    subtitle = glue::glue("{start_date} to {end_date}")
  ) |>
  # format currency
  fmt_currency() |>
  # format date
  fmt_date(columns = date, date_style = "wd_m_day_year") |>
  # format suffixing
  fmt_number(columns = volume, suffixing = TRUE) %>% 
 
  # foot note with link
   tab_source_note(
    gt_hyperlink('Reference', 'https://gt.rstudio.com/')
  ) %>% 

  # make images url to images
  #gt_img_rows(columns = image, img_source = "web", height = 120) %>% 
  # align columns
  cols_align(
  align = c("center"),
  columns = everything()
)
```


## Packages that use or extend gt

There are several R packages that either use gt to generate tabular outputs or extend gt in amazing ways. Here is a short list of some of these great packages:

-   **gtsummary** ([GITHUB](https://github.com/ddsjoberg/gtsummary), [WEBSITE](https://www.danieldsjoberg.com/gtsummary/))

-   **gtExtras** ([GITHUB](https://github.com/jthomasmock/gtExtras), [WEBSITE](https://jthomasmock.github.io/gtExtras/))

-   **pointblank** ([GITHUB](https://github.com/rstudio/pointblank), [WEBSITE](https://rstudio.github.io/pointblank/))

-   **tfrmt** ([GITHUB](https://github.com/GSK-Biostatistics/tfrmt), [WEBSITE](https://gsk-biostatistics.github.io/tfrmt/))

-   **gto** ([GITHUB](https://github.com/GSK-Biostatistics/gto))

## reference:

https://gt.rstudio.com/

# Data table with reactable


```{r}
library(reactable)
library(reactablefmtr)
mtcars %>% reactable()%>% 
  # Main title
  reactablefmtr::add_title(
    title = 'Main title'
  ) %>% 
    # sub title
  reactablefmtr::add_subtitle(
    subtitle = 'sub title',
    font_weight = 'normal'
  )
```

## reference:
https://www.youtube.com/watch?v=E3ubwU5Uyqw



# Data table with kable

```{r}
library(knitr)
mtcars %>% head() %>% kable()
```

## pages data

```{r}
library(rmarkdown)
mtcars %>% paged_table()
```



## reference:

https://rstudio.github.io/distill/tables.html




